---
title: "Using ggvis with knitr and rmarkdown"
output:
  html_document:
    fig_width: 4
    fig_height: 2
---

Try ggvis
=====================
```{r echo=FALSE}
library(knitr)
# Set up default dimensions. Width and height are multiplied by dpi to get
# pixel dimensions.
knitr::opts_chunk$set(fig.width = 4, fig.height = 3)
```

To embed a ggvis plot just call `ggvis`:

```{r, message = FALSE}
library(ggvis)
mtcars %>% ggvis(x = ~wt, y = ~mpg) %>% layer_points()
```


```{r, fig.width = 8, fig.height = 6}
mtcars %>% ggvis(x = ~wt, y = ~mpg) %>%
  layer_points() %>%
  layer_smooths()
```

The Normal Distribution
=======================

The normal (or Gaussian) distribution is defined as follows:

$$latex
f(x;\mu,\sigma^2) = \frac{1}{\sigma\sqrt{2\pi}} 
e^{ -\frac{1}{2}\left(\frac{x-\mu}{\sigma}\right)^2 }
$$

To generate random draws from a normal distribution we use the **rnorm** function:

```{r block1}
output <- rnorm(1000, 100, 15);
```

The normal distribution has the typical bell shape:

```{r block2, fig.width=8, fig.height=5}
library(ggplot2)
qplot(output)
```

## Kernel density estimation

We can perform density estimation on the sample:

```{r block3, fig.width=8, fig.height=5}
plot(density(output))
``` 

## Carl Friedrich Gauss

This little guy had something to do with it

!['Gauss'](https://goo.gl/eXN77h)


